\usepackage{listings}
\usepackage{textcomp}
\usepackage{fancyvrb}

\title{Challenges of Giving Tutorials at PyCon}
\author{Moshe Zadka -- https://cobordism.com}
\date{2020}

\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}

\frame{\titlepage}

\begin{frame}
\frametitle{Acknowledgement of Country}

San Francisco Bay Area

Ancestral home of the Muweka Ohlone
\end{frame}

\begin{frame}
\frametitle{Conference Tutorials}

\begin{itemize}
\item In-person conferences
\item Just before main talks
\item Cost: \$500+
\item Time: around 3 hours
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Diversity is good}

\begin{itemize}
\item Ethnic
\item Race
\item Gender
\item Orientation
\item Religion
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Diversity is not so good...}

\begin{itemize}
\item Experience
\item Sub-speciality
\item Knowledge
\item Infrastructure
\item Goals
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{OS Diversity}

\begin{itemize}
\item Mac OS X: Which version
\item Windows: Version + Home/Pro/other exotic + Managed
\item Linux: There's alsways someone with Gentoo
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Installing Python}

\begin{itemize}
\item No, no Python 2
\item App Store?
\item Installer from Python.org?
\item Pyenv
\item Conda forge
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Installing Python Redux}

Installing software on modern desktop operating systems is impossible.

\end{frame}

\begin{frame}
\frametitle{Setting up Python}

\begin{itemize}
\item Set up a virtual env...
\item ...unless you're on conda
\item Instructions differ per OS/Python installer
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Setting up environment}

\begin{itemize}
\item Activate virtuale environment and \verb|pip install -r requirements|
      \pause
\item Except there's no binary wheel for this package for Linux.
      \pause
\item Here's how you install Python binary package build deps
      \pause
\item ...on Ubuntu...
      \pause
\item ...or Fedora
      \pause
\item This other package does not have a windows wheel
      \pause
\item ...here's how you install the free version of Visual Studio
      \pause
\item This other package does not have a Mac OS X wheel
      \pause
\item ...OK to install XCode you need to click yes on the EULA
      \pause
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Instructions Beforehand}

\begin{itemize}
\item <50% of the class will do them
      \pause
\item Ever wanted to debug visual studio on Windows 10 Home
      without SP1 not building Twisted over e-mail?
      \pause
\item ...No?
      \pause
\item Too bad, because you just got an e-mail about it
      \pause
\item Hooray, another e-mail because your first guess didn't work.
      Also, guy who paid \$500 is now mad at you.
      \pause
\item Your second guess didn't work?
      Get ready to spend 2 hours on Googling.
      Now guy who paid \$500 has cost you 2 extra hours,
      and is really mad at you.
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Installing in class}

\begin{itemize}
\item Asking a volunteer to TA something you get paid for feels icky
      \pause
\item ...but those $1000 you get go really fast if you pay a TA
      \pause
\item ...and debugging Windows 10 Home without SP1 not building Twisted
      is not much more fun in person
      \pause
\item And also someone is missing class, so they're mad.
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Machine abstractions}

\begin{frame}
\item Using Docker? Now you have two problems
\item VirtualBox? Three problems
\item Ever tried to download a 1GB image over conference wifi?
\end{frame}

\end{frame}

\begin{frame}
\frametitle{No time to know students}

Not even their names!
\end{frame}

\begin{frame}
\frametitle{Knowledge diversity}

"Intermediate" is not a thing.

\end{frame}

\begin{frame}
\frametitle{Experience diversity}

Ops? Debugging? Algorithms?

\end{frame}


\begin{frame}
\frametitle{Outcome diversity}

\begin{itemize}
\item Spend time playing with new tech
\item Job skills
\item Interview skills
\item Building portfolio
\item Dunno, job paid for me.
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Sub-speciality diversity}

A data scientist, site reliability engineer,
and a web developer walk into a tutorial...

\end{frame}

\begin{frame}
\frametitle{Economics}

\begin{itemize}
\item Price: $500
\item Paid: $1000
\item Investment: giving tutorial (3hr, but often kills full work day)
\item Investment: prep (3hr practice talk, 2hr+ comms beforehand, 10hrs writing and research)
\item $50/hr to give so-so experience
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Summary}

\begin{itemize}

\item High cost
\item Low reward
\item One shot
\end{itemize}

\end{frame}

\end{document}
